---
title: "Language models accurately infer correlations between psychological items and scales from text alone"
date: "2023-11-07"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{css, echo=FALSE}
summary {
  display: block;
  margin-bottom: 2em;
}

summary h3, summary h4 {
  display: list-item;
}
```

Here, we apply the pre-trained model and our fine-tuned model to data not used for training, a holdout. The holdout sample was collected by Bainbridge et al. 2022.

```{r warning=F,message=F}
knitr::opts_chunk$set(echo = TRUE, error = T, message = F, warning = F)

# Libraries and Settings

# Libs ---------------------------
library(knitr)
library(tidyverse)
library(arrow)
library(glue)
library(psych)
library(lavaan)
library(ggplot2)
library(plotly)
library(gridExtra)
library(broom)
library(broom.mixed)
library(brms)
library(tidybayes)
library(cmdstanr)
library(cowplot)

options(mc.cores = parallel::detectCores(), 
        brms.backend = "cmdstanr", 
        brms.file_refit = "on_change")


model_name = "ItemSimilarityTraining-20240502-trial12"
#model_name = "item-similarity-20231018-122504"
pretrained_model_name = "all-mpnet-base-v2"

data_path = glue("./")
pretrained_data_path = glue("./")

set.seed(42)


holdout <- arrow::read_feather(file = file.path(data_path, glue("ignore.{model_name}.raw.osf-bainbridge-2021-s2-0.item_correlations.feather")))

pt_holdout <- arrow::read_feather(file = file.path(data_path, glue("ignore.{pretrained_model_name}.raw.osf-bainbridge-2021-s2-0.item_correlations.feather")))

holdout_mapping_data = arrow::read_feather(
  file = file.path(data_path, glue("{model_name}.raw.osf-bainbridge-2021-s2-0.mapping2.feather"))
) %>%
  rename(scale_0 = scale0,
         scale_1 = scale1)

holdout_human_data = arrow::read_feather(
  file = file.path(data_path, glue("{model_name}.raw.osf-bainbridge-2021-s2-0.human.feather"))
)

holdout_scales <- arrow::read_feather(file.path(data_path, glue("{model_name}.raw.osf-bainbridge-2021-s2-0.scales.feather"))
)

N <- holdout_human_data %>% summarise_all(~ sum(!is.na(.))) %>% min()
total_N <- nrow(holdout_human_data)
```

The Bainbridge data was collected on N=`r total_N` respondents. The item with the most missing values still had n=`r N`.


## Synthetic inter-item correlations
```{r}
holdout_llm <- holdout %>%
  left_join(holdout_mapping_data %>% select(variable_1 = variable, InstrumentA = instrument, ScaleA = scale_0, SubscaleA = scale_1)) %>%
  left_join(holdout_mapping_data %>% select(variable_2 = variable, InstrumentB = instrument, ScaleB = scale_0, SubscaleB = scale_1))

pt_holdout_llm <- pt_holdout %>%
  left_join(holdout_mapping_data %>% select(variable_1 = variable, InstrumentA = instrument, ScaleA = scale_0, SubscaleA = scale_1)) %>%
  left_join(holdout_mapping_data %>% select(variable_2 = variable, InstrumentB = instrument, ScaleB = scale_0, SubscaleB = scale_1))
```


### Accuracy
```{r}
se2 <- mean(holdout_llm$empirical_r_se^2)

r <- broom::tidy(cor.test(holdout_llm$empirical_r, holdout_llm$synthetic_r))
pt_r <- broom::tidy(cor.test(pt_holdout_llm$empirical_r, pt_holdout_llm$synthetic_r))

model <- paste0('
  # Latent variables
  PearsonLatent =~ 1*empirical_r

  # Fixing error variances based on known standard errors
  empirical_r ~~ ',se2,'*empirical_r

  # Relationship between latent variables
  PearsonLatent ~~ synthetic_r
')

fit <- sem(model, data = holdout_llm)
pt_fit <- sem(model, data = pt_holdout_llm)

m_synth_r_items <- brm(
  bf(empirical_r | mi(empirical_r_se) ~ synthetic_r + (1|mm(variable_1, variable_2)),
     sigma ~ poly(synthetic_r, degree = 3)), data = holdout_llm, 
  file = "ignore/m_synth_r_items_lm")

sd_synth <- sd(m_synth_r_items$data$synthetic_r)

newdata <- m_synth_r_items$data %>% select(empirical_r, synthetic_r, empirical_r_se)
epreds <- epred_draws(newdata = newdata, obj = m_synth_r_items, re_formula = NA, ndraws = 200)
preds <- predicted_draws(newdata = newdata, obj = m_synth_r_items, re_formula = NA, ndraws = 200)
epred_preds <- epreds %>% left_join(preds)
by_draw <- epred_preds %>% group_by(.draw) %>% 
  summarise(.epred = var(.epred),
            .prediction = var(.prediction),
            sigma = sqrt(.prediction - .epred),
            semi_latent_r = sqrt(.epred/.prediction))
rm(epred_preds)

accuracy_bayes_items <- by_draw %>% mean_hdci(semi_latent_r)

bind_rows(
  pt_r %>% 
    mutate(model = "pre-trained", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  standardizedsolution(pt_fit) %>% 
    filter(lhs == "PearsonLatent", rhs ==  "synthetic_r") %>% 
    mutate(model = "pre-trained", kind = "semi-latent (SEM)") %>% 
    select(model, kind, accuracy = est.std, 
           conf.low = ci.lower, conf.high = ci.upper),
  r %>% 
    mutate(model = "fine-tuned", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  standardizedsolution(fit) %>% 
    filter(lhs == "PearsonLatent", rhs ==  "synthetic_r") %>% 
    mutate(model = "fine-tuned", kind = "semi-latent (SEM)") %>% 
    select(model, kind, accuracy = est.std, 
           conf.low = ci.lower, conf.high = ci.upper),
  accuracy_bayes_items %>% 
    mutate(model = "fine-tuned", kind = "semi-latent (Bayesian EIV)") %>% 
    select(model, kind, accuracy = semi_latent_r, conf.low = .lower, conf.high = .upper)
  ) %>% 
  knitr::kable(digits = 2)
```


<details><summary><h4>Prediction error plot according to synthetic estimate</h4></summary>

```{r}
m_synth_r_items

pred <- conditional_effects(m_synth_r_items, method = "predict")
by_draw %>% mean_hdci(sigma)
plot(conditional_effects(m_synth_r_items, dpar = "sigma"), plot = F)[[1]] + 
  theme_bw() + 
  ylab("Prediction error (sigma)")
```

</details>



### Scatter plot
```{r}
ggplot(holdout_llm, aes(synthetic_r, empirical_r, 
              ymin = empirical_r - empirical_r_se,
              ymax = empirical_r + empirical_r_se)) + 
  geom_abline(linetype = "dashed") +
  geom_point(color = "#00A0B0", alpha = 0.1, size = 1) +
  geom_smooth(aes(
    x = synthetic_r,
    y = estimate__,
    ymin = lower__,
    ymax = upper__,
  ), stat = "identity", 
  color = "#a48500",
  fill = "#EDC951",
  data = as.data.frame(pred$synthetic_r)) +
  xlab("Synthetic inter-item correlation") + 
  ylab("Empirical inter-item correlation") +
  theme_bw() +
  coord_fixed(xlim = c(-1,1), ylim = c(-1,1)) -> plot_items
plot_items
```

### Interactive plot
This plot shows only 2000 randomly selected item pairs to conserve memory. A [full interactive plot](2_interactive_item_plot.html) exists, but may react slowly.

```{r}
item_pair_table <- holdout_llm %>% 
   left_join(holdout_mapping_data %>% select(variable_1 = variable,
                                             item_text_1 = item_text)) %>% 
   left_join(holdout_mapping_data %>% select(variable_2 = variable,
                                             item_text_2 = item_text))

# item_pair_table %>% filter(str_length(item_text_1) < 30, str_length(item_text_2) < 30) %>% 
#   left_join(pt_holdout_llm %>% rename(synthetic_r_pt = synthetic_r)) %>% 
#   select(item_text_1, item_text_2, empirical_r, synthetic_r, synthetic_r_pt) %>% View()
rio::export(item_pair_table, "ignore/item_pair_table.feather")

(item_pair_table %>% 
  mutate(synthetic_r = round(synthetic_r, 2),
         empirical_r = round(empirical_r, 2),
         items = str_replace_all(str_c(item_text_1, "\n", item_text_2),
                                  "_+", " ")) %>% 
    sample_n(2000) %>%
ggplot(., aes(synthetic_r, empirical_r, 
              # ymin = empirical_r - empirical_r_se, 
              # ymax = empirical_r + empirical_r_se, 
              label = items)) + 
  geom_abline(linetype = "dashed") +
  geom_point(color = "#00A0B0", alpha = 0.3, size = 1) +
  xlab("Synthetic inter-item correlation") + 
  ylab("Empirical inter-item correlation") +
  theme_bw() +
  coord_fixed(xlim = c(-1,1), ylim = c(-1,1))) %>% 
  ggplotly()

item_pair_table <- item_pair_table %>% 
  mutate(empirical_r = sprintf("%.2f±%.3f", empirical_r,
                                 empirical_r_se),
           synthetic_r = sprintf("%.2f", synthetic_r)) %>% 
  select(item_text_1, item_text_2, empirical_r, synthetic_r)
rio::export(item_pair_table, "item_pair_table.xlsx")
```

<details><summary><h3>Robustness checks</h3></summary>


Is the accuracy lower within/across scales and instruments?

```{r}
holdout_llm %>% 
  mutate(same_instrument = if_else(InstrumentA == InstrumentB, 1, 0,0),
         same_scale = if_else(ScaleA == ScaleB, 1,0,0),
         same_subscale = if_else(same_scale & SubscaleA == SubscaleB, 1,0,0)) %>% 
  group_by(same_scale, same_instrument, same_subscale) %>% 
  summarise(broom::tidy(cor.test(synthetic_r, empirical_r)), sd_emp_r = sd(empirical_r), n = n()) %>% 
  select(same_instrument, same_scale, same_subscale, r = estimate, conf.low, conf.high, n, sd_emp_r) %>% 
  arrange(same_instrument, same_scale, same_subscale) %>% 
  kable()
```

Is the accuracy lower outside classic Big Five?

```{r}
holdout_llm %>% 
  mutate(big_five = case_when(
    str_detect(InstrumentA, "(Personality|Big Five)") & str_detect(InstrumentB, "(Personality|Big Five)") ~ "both",
    str_detect(InstrumentA, "(Personality|Big Five)") | str_detect(InstrumentB, "(Personality|Big Five)") ~ "either",
    TRUE ~ "none"
         )) %>% 
  group_by(big_five) %>% 
  summarise(broom::tidy(cor.test(synthetic_r, empirical_r)), sd_emp_r = sd(empirical_r), n = n()) %>% 
  select(big_five, r = estimate, conf.low, conf.high, n, sd_emp_r) %>% 
  arrange(big_five) %>% 
  kable()
```

Is the accuracy lower for items that have low variance?

```{r}
item_variances <- holdout_human_data %>% summarise_all(~ sd(., na.rm = T)) %>% 
  pivot_longer(everything(), names_to = "variable", values_to = "item_sd")

by_max_cov <- holdout_llm %>% 
  left_join(item_variances, by = c("variable_1" = "variable")) %>% 
  left_join(item_variances, by = c("variable_2" = "variable"), suffix = c("_1", "_2")) %>% 
  mutate(max_covariance = ceiling((item_sd_1 * item_sd_2)*10)/10)

rs_by_max_cov <- by_max_cov %>% 
  group_by(max_covariance) %>% 
  filter(n() > 3) %>% 
  summarise(broom::tidy(cor.test(synthetic_r, empirical_r)), sd_emp_r = sd(empirical_r), n = n()) %>% 
  select(max_covariance, r = estimate, conf.low, conf.high, n, sd_emp_r) %>% 
  arrange(max_covariance)

rs_by_max_cov%>% 
  kable()
rs_by_max_cov %>% ggplot(aes(max_covariance, r, ymin = conf.low, ymax = conf.high)) +
  geom_pointrange()

by_max_cov%>% 
  filter(max_covariance > .7) %>% 
  summarise(broom::tidy(cor.test(synthetic_r, empirical_r)), sd_emp_r = sd(empirical_r), n = n()) %>% 
  kable()

holdout_llm %>% 
  left_join(item_variances, by = c("variable_1" = "variable")) %>% 
  left_join(item_variances, by = c("variable_2" = "variable"), suffix = c("_1", "_2")) %>% 
  mutate(max_covariance = ceiling((item_sd_1 * item_sd_2)*10)/10) %>% 
  filter(max_covariance > 1) %>% 
  summarise(broom::tidy(cor.test(synthetic_r, empirical_r)), sd_emp_r = sd(empirical_r), n = n()) %>% 
  select(r = estimate, conf.low, conf.high, n, sd_emp_r) %>% 
  knitr::kable()
```



Is the accuracy lower for the pre-trained model?

```{r}
ggplot(pt_holdout_llm, aes(synthetic_r, empirical_r, 
              ymin = empirical_r - empirical_r_se,
              ymax = empirical_r + empirical_r_se)) + 
  geom_abline(linetype = "dashed") +
  geom_point(color = "#00A0B0", alpha = 0.1, size = 1) +
  xlab("Synthetic inter-item correlation") + 
  ylab("Empirical inter-item correlation") +
  theme_bw() +
  coord_fixed(xlim = c(-1,1), ylim = c(-1,1)) -> pt_plot_items
pt_plot_items
```


</details>



[Full table of synthetic and empirical item pair correlations](item_pair_table.xlsx)


## Synthetic Reliabilities
```{r}
cors_llm <- holdout_llm %>%
  select(x = variable_1, y = variable_2, r = synthetic_r) %>%
  as.data.frame() |>
  igraph::graph_from_data_frame(directed = FALSE) |>
  igraph::as_adjacency_matrix(attr = "r", sparse = FALSE)
diag(cors_llm) <- 1

pt_cors_llm <- pt_holdout_llm %>%
  select(x = variable_1, y = variable_2, r = synthetic_r) %>%
  as.data.frame() |>
  igraph::graph_from_data_frame(directed = FALSE) |>
  igraph::as_adjacency_matrix(attr = "r", sparse = FALSE)
diag(pt_cors_llm) <- 1

cors_real <- holdout_llm %>%
  select(x = variable_1, y = variable_2, r = empirical_r) %>%
  as.data.frame() |>
  igraph::graph_from_data_frame(directed = FALSE) |>
  igraph::as_adjacency_matrix(attr = "r", sparse = FALSE)
diag(cors_real) <- 1

mapping_data <- holdout_mapping_data
items_by_scale <- bind_rows(
  holdout_scales %>% filter(scale_1 == "") %>% left_join(mapping_data %>% select(-scale_1), by = c("instrument", "scale_0")),
  holdout_scales %>% filter(scale_1 != "") %>% left_join(mapping_data, by = c("instrument", "scale_0", "scale_1"))
)
  
scales <- items_by_scale %>%
  group_by(keyed, scale) %>%
  summarise(
    items = list(variable),
    number_of_items = n_distinct(variable),
    lvn = paste(first(scale), " =~ ", paste(variable, collapse = " + "))) %>%
  drop_na() %>% 
  ungroup()


random_scales <- list()
for(i in 1:200) {
  n_items <- rpois(1, mean(scales$number_of_items))
  n_items <- if_else(n_items < 3, 3, n_items)
  random_scales[[i]] <- holdout_mapping_data %>%
    sample_n(n_items) %>%
    mutate(scale = paste0("random", i)) %>%
    group_by(scale) %>%
    summarise(
      items = list(variable),
      number_of_items = n_distinct(variable),
      lvn = paste(first(scale), " =~ ", paste(variable, collapse = " + "))) %>%
    drop_na() %>% 
    mutate(keyed = 1)
}

random_scales <- bind_rows(random_scales)
scales <- bind_rows(scales, random_scales)

source("global_functions.R")

scales <- scales %>% filter(number_of_items >= 3)

scales <- scales %>%
  rowwise() %>%
  mutate(r_real = list(cors_real[items, items]),
         pt_r_llm = list(pt_cors_llm[items, items]),
         r_llm = list(cors_llm[items, items])) %>%
  mutate(reverse_items = list(find_reverse_items_by_first_item(r_real, keyed)),
         r_real_rev = list(reverse_items(r_real, reverse_items)),
         pt_r_llm_rev = list(reverse_items(pt_r_llm, reverse_items)),
         r_llm_rev = list(reverse_items(r_llm, reverse_items))) %>%
  mutate(
    rel_real = list(psych::alpha(r_real_rev, keys = F, n.obs = N)$feldt),
    rel_llm = list(psych::alpha(r_llm_rev, keys = F, n.obs = N)$feldt),
    rel_pt_llm = list(psych::alpha(pt_r_llm_rev, keys = F, n.obs = N)$feldt)) %>%
  mutate(empirical_alpha = rel_real$alpha$raw_alpha,
         synthetic_alpha = rel_llm$alpha$raw_alpha,
         pt_synthetic_alpha = rel_pt_llm$alpha$raw_alpha) %>%
  mutate(
    empirical_alpha_se = mean(diff(unlist(psychometric::alpha.CI(empirical_alpha, k = number_of_items, N = N, level = 0.95))))
  )

scales <- scales %>% filter(empirical_alpha > 0)
# qplot(scales$empirical_alpha_se)
# qplot(scales$empirical_alpha, scales$empirical_alpha_se)
# qplot(scales$number_of_items, scales$empirical_alpha_se)
# qplot(scales$empirical_alpha, scales$empirical_alpha_se, color = scales$number_of_items)
```


### Accuracy
```{r}
se2 <- mean(scales$empirical_alpha_se^2)
r <- broom::tidy(cor.test(scales$empirical_alpha, scales$synthetic_alpha))
pt_r <- broom::tidy(cor.test(scales$empirical_alpha, scales$pt_synthetic_alpha))

model <- paste0('
  # Latent variables
  latent_real_rel =~ 1*empirical_alpha

  # Fixing error variances based on known standard errors
  empirical_alpha ~~ ',se2,'*empirical_alpha

  # Relationship between latent variables
  latent_real_rel ~~ synthetic_alpha
')

fit <- sem(model, data = scales)
pt_fit <- sem(model, data = scales %>% 
                select(empirical_alpha, synthetic_alpha = pt_synthetic_alpha))

m_lmsynth_rel_scales <- brm(
  bf(empirical_alpha | mi(empirical_alpha_se) ~ synthetic_alpha,
     sigma ~ poly(synthetic_alpha, degree = 3)), data = scales, 
  file = "ignore/m_synth_rel_lm")

newdata <- m_lmsynth_rel_scales$data %>% select(empirical_alpha, synthetic_alpha, empirical_alpha_se)
epreds <- epred_draws(newdata = newdata, obj = m_lmsynth_rel_scales, re_formula = NA)
preds <- predicted_draws(newdata = newdata, obj = m_lmsynth_rel_scales, re_formula = NA)
epred_preds <- epreds %>% left_join(preds)
by_draw <- epred_preds %>% group_by(.draw) %>% 
  summarise(.epred = var(.epred),
            .prediction = var(.prediction),
            sigma = sqrt(.prediction - .epred),
            semi_latent_r = sqrt(.epred/.prediction))

accuracy_bayes_rels <- by_draw %>% mean_hdci(semi_latent_r)

bind_rows(
  pt_r %>% 
    mutate(model = "pre-trained", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  standardizedsolution(pt_fit) %>% 
    filter(lhs == "latent_real_rel", rhs ==  "synthetic_alpha") %>% 
    mutate(model = "pre-trained", kind = "semi-latent (SEM)") %>% 
    select(model, kind, accuracy = est.std, 
           conf.low = ci.lower, conf.high = ci.upper),
  r %>% 
    mutate(model = "fine-tuned", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  standardizedsolution(fit) %>% 
    filter(lhs == "latent_real_rel", rhs ==  "synthetic_alpha") %>% 
    mutate(model = "fine-tuned", kind = "semi-latent (SEM)") %>% 
    select(model, kind, accuracy = est.std, 
           conf.low = ci.lower, conf.high = ci.upper),
  accuracy_bayes_rels %>% 
    mutate(model = "fine-tuned", kind = "semi-latent (Bayesian EIV)") %>% 
    select(model, kind, accuracy = semi_latent_r, conf.low = .lower, conf.high = .upper)
  ) %>% 
  knitr::kable(digits = 2)
```


<details><summary><h4>Prediction error plot according to synthetic estimate</h4></summary>

```{r}
m_lmsynth_rel_scales

pred <- conditional_effects(m_lmsynth_rel_scales, method = "predict")
by_draw %>% 
  filter(!is.nan(sigma)) %>% mean_hdci(sigma)

plot(conditional_effects(m_lmsynth_rel_scales, dpar = "sigma"), plot = F)[[1]] + 
  theme_bw() + 
  scale_x_continuous(limits = c(0,1))+
  scale_y_continuous(limits = c(0,0.13)) +
  ylab("Prediction error (sigma)")
```

</details>




### Scatter plot
```{r}
ggplot(scales, aes(synthetic_alpha, empirical_alpha, 
                   color = str_detect(scale, "^random"), 
              ymin = empirical_alpha - empirical_alpha_se,
              ymax = empirical_alpha + empirical_alpha_se)) + 
  geom_abline(linetype = "dashed") +
  geom_point(alpha = 0.6, size = 1) +
  geom_smooth(aes(
    x = synthetic_alpha,
    y = estimate__,
    ymin = lower__,
    ymax = upper__,
  ), stat = "identity", 
  color = "#a48500",
  fill = "#EDC951",
  data = as.data.frame(pred$synthetic_alpha)) +
  scale_color_manual(values = c("#00A0B0", "#6A4A3C"),
                     guide = "none") +
  xlab("Synthetic Cronbach's alpha") + 
  ylab("Empirical Cronbach's alpha") +
  theme_bw() +
  coord_fixed(xlim = c(0,1), ylim = c(0,1)) -> plot_rels
plot_rels
```

### Interactive plot
```{r}
(scales %>% 
  filter(!str_detect(scale, "^random")) %>% 
  mutate(synthetic_alpha = round(synthetic_alpha, 2),
         empirical_alpha = round(empirical_alpha, 2),
         scale = str_replace_all(scale, "_+", " ")) %>% 
ggplot(., aes(synthetic_alpha, empirical_alpha, 
              # ymin = empirical_r - empirical_r_se, 
              # ymax = empirical_r + empirical_r_se, 
              label = scale)) + 
  geom_abline(linetype = "dashed") +
  geom_point(alpha = 0.3, size = 1, color = "#00A0B0") +
  xlab("Synthetic Cronbach's alpha") + 
  ylab("Empirical Cronbach's alpha") +
  theme_bw() +
  theme(legend.position='none') + 
  coord_fixed(xlim = c(NA,1), ylim = c(NA,1))) %>% 
  ggplotly()
```

<details><summary><h4>Table</h4></summary>

```{r}
scales %>% 
  filter(!str_detect(scale, "^random")) %>% 
  mutate(empirical_alpha = sprintf("%.2f±%.3f", empirical_alpha,
                               empirical_alpha_se),
         synthetic_alpha = sprintf("%.2f", synthetic_alpha),
         scale = str_replace_all(scale, "_+", " ")
         ) %>% 
  select(scale, empirical_alpha, synthetic_alpha, number_of_items) %>% 
  DT::datatable(rownames = FALSE,
                filter = "top")
```

</details>



<details><summary><h3>Robustness checks</h3></summary>

```{r}
scales %>% 
  group_by(str_detect(scale, "^random")) %>% 
  summarise(broom::tidy(cor.test(synthetic_alpha, empirical_alpha)), sd_alpha = sd(empirical_alpha), n = n()) %>% 
  knitr::kable()
```


Although the number of items alone can of course predict Cronbach's alpha, the synthetic alphas explain much more variance in empirical alphas.

```{r}
scales %>% 
  ungroup() %>% 
  summarise(broom::tidy(cor.test(number_of_items, empirical_alpha)), sd_alpha = sd(empirical_alpha), n = n()) %>% 
  knitr::kable()


summary(lm(empirical_alpha ~ number_of_items, scales))
summary(lm(empirical_alpha ~ number_of_items + synthetic_alpha, scales))
```



Is the accuracy lower for the pre-trained model?

```{r}
ggplot(scales, aes(pt_synthetic_alpha, empirical_alpha, 
                   color = str_detect(scale, "^random"), 
              ymin = empirical_alpha - empirical_alpha_se,
              ymax = empirical_alpha + empirical_alpha_se)) + 
  geom_abline(linetype = "dashed") +
  geom_point(alpha = 0.6, size = 1) +
  scale_color_manual(values = c("#00A0B0", "#6A4A3C"),
                     guide = "none") +
  xlab("Synthetic Cronbach's alpha") + 
  ylab("Empirical Cronbach's alpha") +
  theme_bw() +
  coord_fixed(xlim = c(0,1), ylim = c(0,1)) -> pt_plot_rels
pt_plot_rels
```


</details>




## Synthetic Scale Correlations
```{r}
manifest_scores = arrow::read_feather(file = file.path(data_path, glue("ignore.{model_name}.raw.osf-bainbridge-2021-s2-0.scale_correlations.feather")))
pt_manifest_scores = arrow::read_feather(file = file.path(data_path, glue("ignore.{pretrained_model_name}.raw.osf-bainbridge-2021-s2-0.scale_correlations.feather")))

n_distinct(manifest_scores$scale_a)

manifest_scores <- manifest_scores %>%
 left_join(scales, by = c("scale_a" = "scale")) %>%
 left_join(scales, by = c("scale_b" = "scale"))
```

### Accuracy
```{r}
r <- broom::tidy(cor.test(manifest_scores$empirical_r, manifest_scores$synthetic_r))
pt_r <- broom::tidy(cor.test(pt_manifest_scores$empirical_r, pt_manifest_scores$synthetic_r))

se2 <- mean(manifest_scores$empirical_r_se^2)
model <- paste0('
    # Latent variables
    PearsonLatent =~ 1*empirical_r

    # Fixing error variances based on known standard errors
    empirical_r ~~ ',se2,'*empirical_r

    # Relationship between latent variables
    PearsonLatent ~~ synthetic_r
  ')

fit <- sem(model, data = manifest_scores)
pt_fit <- sem(model, data = pt_manifest_scores)


m_lmsynth_r_scales <- brm(
  bf(empirical_r | mi(empirical_r_se) ~ synthetic_r + (1|mm(scale_a, scale_b)),
     sigma ~ poly(synthetic_r, degree = 3)), data = manifest_scores, 
  file = "ignore/m_synth_r_scales_lm8")

sd_synth <- sd(m_lmsynth_r_scales$data$synthetic_r)


newdata <- m_lmsynth_r_scales$data %>% select(empirical_r, synthetic_r, empirical_r_se)
epreds <- epred_draws(newdata = newdata, obj = m_lmsynth_r_scales, re_formula = NA)
preds <- predicted_draws(newdata = newdata, obj = m_lmsynth_r_scales, re_formula = NA)
epred_preds <- epreds %>% left_join(preds)
by_draw <- epred_preds %>% group_by(.draw) %>% 
  summarise(.epred = var(.epred),
            .prediction = var(.prediction),
            sigma = sqrt(.prediction - .epred),
            semi_latent_r = sqrt(.epred/.prediction))

accuracy_bayes_scales <- by_draw %>% mean_hdci(semi_latent_r)

bind_rows(
  pt_r %>% 
    mutate(model = "pre-trained", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  standardizedsolution(pt_fit) %>% 
    filter(lhs == "PearsonLatent", rhs ==  "synthetic_r") %>% 
    mutate(model = "pre-trained", kind = "semi-latent (SEM)") %>% 
    select(model, kind, accuracy = est.std, 
           conf.low = ci.lower, conf.high = ci.upper),
  r %>% 
    mutate(model = "fine-tuned", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  standardizedsolution(fit) %>% 
    filter(lhs == "PearsonLatent", rhs ==  "synthetic_r") %>% 
    mutate(model = "fine-tuned", kind = "semi-latent (SEM)") %>% 
    select(model, kind, accuracy = est.std, 
           conf.low = ci.lower, conf.high = ci.upper),
  accuracy_bayes_scales %>% 
    mutate(model = "fine-tuned", kind = "semi-latent (Bayesian EIV)") %>% 
    select(model, kind, accuracy = semi_latent_r, conf.low = .lower, conf.high = .upper)
  ) %>% 
  knitr::kable(digits = 2)
```


<details><summary><h4>Prediction error plot according to synthetic estimate</h4></summary>

```{r}
m_lmsynth_r_scales
by_draw %>% mean_hdci(sigma)

pred <- conditional_effects(m_lmsynth_r_scales, method = "predict")
plot(conditional_effects(m_lmsynth_r_scales, dpar = "sigma"), plot = F)[[1]] + 
  theme_bw() + 
  ylab("Prediction error (sigma)")
```


</details>



### Scatter plot
```{r}
ggplot(manifest_scores, aes(synthetic_r, empirical_r, 
              ymin = empirical_r - empirical_r_se,
              ymax = empirical_r + empirical_r_se)) + 
  geom_abline(linetype = "dashed") +
  geom_point(color = "#00A0B0", alpha = 0.3, size = 1) +
  geom_smooth(aes(
    x = synthetic_r,
    y = estimate__,
    ymin = lower__,
    ymax = upper__,
  ), stat = "identity", 
  color = "#a48500",
  fill = "#EDC951",
  data = as.data.frame(pred$synthetic_r)) +
  xlab("Synthetic inter-scale correlation") + 
  ylab("Empirical inter-scale correlation") +
  theme_bw() +
  coord_fixed(xlim = c(-1,1), ylim = c(-1,1)) -> plot_scales
plot_scales
```

### Interactive plot
```{r}
(manifest_scores %>% 
  mutate(synthetic_r = round(synthetic_r, 2),
         empirical_r = round(empirical_r, 2),
         scales = str_replace_all(str_c(scale_a, "\n", scale_b),
                                  "_+", " ")) %>% 
ggplot(., aes(synthetic_r, empirical_r, 
              # ymin = empirical_r - empirical_r_se, 
              # ymax = empirical_r + empirical_r_se, 
              label = scales)) + 
  geom_abline(linetype = "dashed") +
  geom_point(color = "#00A0B0", alpha = 0.3, size = 1) +
  xlab("Synthetic inter-scale correlation") + 
  ylab("Empirical inter-scale correlation") +
  theme_bw() +
  coord_fixed(xlim = c(-1,1), ylim = c(-1,1))) %>% 
  ggplotly()
```

<details><summary>Table</summary>

```{r}
manifest_scores %>% 
                mutate(empirical_r = sprintf("%.2f±%.3f", empirical_r,
                                             empirical_r_se),
                       synthetic_r = sprintf("%.2f", synthetic_r),
                       scale_a = str_replace_all(scale_a, "_+", " "),
                       scale_b = str_replace_all(scale_b, "_+", " ")
                       ) %>% 
                select(scale_a, scale_b, empirical_r, synthetic_r) %>% 
  DT::datatable(rownames = FALSE,
                filter = "top")
```

</details>




<details><summary><h3>Robustness checks</h3></summary>

How does number of items across the two scales relate to accuracy?

```{r}
by_item_number <- manifest_scores %>%
  mutate(items = number_of_items.x + number_of_items.y) %>%
  group_by(items) %>%
  summarise(broom::tidy(cor.test(empirical_r, synthetic_r)), pairwise_n = n()) 

by_item_number %>% 
  ggplot(aes(items, estimate, ymin = conf.low, ymax = conf.high)) + 
  geom_pointrange() +
  scale_y_continuous("Manifest accuracy (with 95% confidence interval)") +
  xlab("Number of items summed across scales")

lm(estimate ~ items, by_item_number, weights = 1/(by_item_number$conf.high-by_item_number$conf.low))

manifest_scores %>%
  filter(number_of_items.x >= 10, number_of_items.y >= 10) %>%
  summarise(cor = cor(empirical_r, synthetic_r), n())
```


Is the accuracy lower for the pre-trained model?

```{r}
ggplot(pt_manifest_scores, aes(synthetic_r, empirical_r, 
              ymin = empirical_r - empirical_r_se,
              ymax = empirical_r + empirical_r_se)) + 
  geom_abline(linetype = "dashed") +
  geom_point(color = "#00A0B0", alpha = 0.3, size = 1) +
  xlab("Synthetic inter-scale correlation") + 
  ylab("Empirical inter-scale correlation") +
  theme_bw() +
  coord_fixed(xlim = c(-1,1), ylim = c(-1,1)) -> pt_plot_scales
pt_plot_scales
```


</details>




## Combined plot

```{r fig.width = 8.3, fig.height = 6}
library(patchwork)
pt_plot_items2 <- pt_plot_items +
    annotate("text", size = 2.5, x = 0.5, y = -0.8, vjust = 1, hjust = 1, label = "r(I fear for the worst,\nI never worry about anything)", color = "#00A0B0") +
  annotate("segment", x = 0, y = -0.78, xend = 0.2761906, yend = -0.3459711, color = "#00A0B0", alpha = 0.7) +
  annotate("text", size = 2.5, x = -.1, y = 0.5, hjust = 1, label = "r(I get angry easily,\nI lose my temper)", color = "#00A0B0") + 
  annotate("segment", x = -.1, y = 0.5, xend = 0.6935711, yend = 0.7140546, color = "#00A0B0", alpha = 0.7)
  

plot_items2 <- plot_items +
  annotate("text", size = 3, x = -1, y = 0.98, vjust = 0, hjust = 0, label = with(accuracy_bayes_items, { sprintf("accuracy = %.2f [%.2f;%.2f]", semi_latent_r, .lower, .upper) })) +
  annotate("text", size = 2.5, x = 0.5, y = -0.8, vjust = 1, hjust = 1, label = "r(I fear for the worst,\nI never worry about anything)", color = "#00A0B0") +
  annotate("segment", x = 0, y = -0.78, xend = -0.1104686, yend = -0.3459711, color = "#00A0B0", alpha = 0.7) +
  annotate("text", size = 2.5, x = -.1, y = 0.5, hjust = 1, label = "r(I get angry easily,\nI lose my temper)", color = "#00A0B0") + 
  annotate("segment", x = -.1, y = 0.5, xend = 0.8031979, yend = 0.7140546, color = "#00A0B0", alpha = 0.7)
  # annotate("text", size = 2.5, x = -0.5, y = -0.8, hjust = 0, label = "r(I love life,\nI avoid crowds)", color = "#00A0B0") +
  # annotate("segment", x = -.3, y = -0.7, xend = -0.23, yend = -0.28, color = "#00A0B0", alpha = 0.7) +
  # annotate("text", size = 2.5, x = -.3, y = 0.5, hjust = 1, label = "r(I work hard,\nI am diligent)", color = "#00A0B0") +
  # annotate("segment", x = -.3, y = .5, xend = .52, yend = .58, color = "#00A0B0", alpha = 0.7)


pt_plot_rels2 <- pt_plot_rels + 
  annotate("text", size = 2.5, x = 0.61, y = 0.25, hjust = 0, label = "IPIP Extraversion", color = "#00A0B0") +
  annotate("segment", x = 0.7, y = 0.27, xend = 0.9, yend = 0.90, color = "#00A0B0", alpha = 0.7) +
  annotate("text", size = 2.5, x = -0.02, y = 0.95, hjust = 0, label = "LOT Optimism", color = "#00A0B0") +
  annotate("segment", x = 0.11, y = 0.93, xend = -1.477226, yend = 0.71, color = "#00A0B0", alpha = 0.7)

plot_rels2 <- plot_rels + 
  annotate("text", size = 3, x = 0, y = .985, vjust = 0, hjust = 0, label = with(accuracy_bayes_rels, { sprintf("accuracy = %.2f [%.2f;%.2f]", semi_latent_r, .lower, .upper) })) +
  annotate("text", size = 2.5, x = 0.4, y = 0.1, hjust = 0, label = "randomly formed scales", color = "#6A4A3C") +
  annotate("segment", x = 0.395, y = 0.1, xend = 0.39, yend = 0.4864297, color = "#6A4A3C", alpha = 0.7) +
  annotate("segment", x = 0.395, y = 0.1, xend = 0.285, yend = 0.2279919, color = "#6A4A3C", alpha = 0.7) +
  annotate("segment", x = 0.395, y = 0.1, xend = 0.2, yend = 0.075, color = "#6A4A3C", alpha = 0.7) +
  annotate("text", size = 2.5, x = 0.61, y = 0.4, hjust = 0, label = "IPIP Extraversion", color = "#00A0B0") +
  annotate("segment", x = 0.75, y = 0.42, xend = 0.87, yend = 0.90, color = "#00A0B0", alpha = 0.7) +
  annotate("text", size = 2.5, x = -0.02, y = 0.86, hjust = 0, label = "LOT Optimism", color = "#00A0B0") +
  annotate("segment", x = 0.11, y = 0.83, xend = 0.15, yend = 0.71, color = "#00A0B0", alpha = 0.7)

pt_plot_scales2 <- pt_plot_scales +
  annotate("text", size = 2.5, x = -0.2, y = 0.8, hjust = 1, label = "r(BFI Neuroticism,\nIPIP Neuroticism)", color = "#00A0B0") +
  annotate("segment", x = -.2, y = 0.8, xend = 0.22, yend = .84, color = "#00A0B0", alpha = 0.7) +
  annotate("text", size = 2.5, x = -.1, y = -0.9, hjust = 0, label = "r(BFI Depression facet,\nLOT Optimism)", color = "#00A0B0") +
  annotate("segment", x = -.1, y = -.9, xend = -0.17, yend = -.63, color = "#00A0B0", alpha = 0.7)


plot_scales2 <- plot_scales +
  annotate("text", size = 3, x = -1, y = 0.98, vjust = 0, hjust = 0, label = with(accuracy_bayes_scales, { sprintf("accuracy = %.2f [%.2f;%.2f]", semi_latent_r, .lower, .upper) })) +
  annotate("text", size = 2.5, x = -0.1, y = 0.5, hjust = 1, label = "r(BFI Neuroticism,\nIPIP Neuroticism)", color = "#00A0B0") +
  annotate("segment", x = -.1, y = 0.5, xend = .84, yend = .84, color = "#00A0B0", alpha = 0.7) +
  annotate("text", size = 2.5, x = -.15, y = -0.7, hjust = 0, label = "r(BFI Depression facet,\nLOT Optimism)", color = "#00A0B0") +
  annotate("segment", x = -.15, y = -.7, xend = -.34, yend = -.63, color = "#00A0B0", alpha = 0.7)


(pt_plot_items2+
    pt_plot_rels2 + ggtitle("") +
    pt_plot_scales2) /


(plot_items2 +
    plot_rels2 + ggtitle("SurveyBot 3000")  +
    plot_scales2) +
  plot_annotation(
  title = 'Pre-trained model before domain adaptation and fine-tuning'
)

ggsave("ignore/Figure_pilot.pdf", width = 8.3, height = 6, device = grDevices::cairo_pdf)
ggsave("ignore/Figure_pilot.png", width = 8.3, height = 6)



# ggsave("ignore/Figure_pilot.svg", width = 8.3, height = 5.5, device = svglite::svglite)
```

