---
title: "Language models accurately infer correlations between psychological items and scales from text alone"
date: "2023-11-07"
output: 
  html_document:
    toc: true
    toc_float: true
    css: style.css 
---

Here, we apply the pre-trained model and our fine-tuned model to data not used for training, a holdout. The holdout sample was collected by Bainbridge et al. 2022.

```{r warning=F,message=F}
knitr::opts_chunk$set(echo = TRUE, error = T, message = F, warning = F)

# Libraries and Settings

# Libs ---------------------------
library(knitr)
library(tidyverse)
library(arrow)
library(glue)
library(psych)
library(lavaan)
library(ggplot2)
library(plotly)
library(gridExtra)
library(broom)
library(broom.mixed)
library(brms)
library(tidybayes)
library(cmdstanr)
library(cowplot)

options(mc.cores = parallel::detectCores(), 
        brms.backend = "cmdstanr", 
        brms.file_refit = "on_change")


model_name = "ItemSimilarityTraining-20240502-trial12"
#model_name = "item-similarity-20231018-122504"
pretrained_model_name = "all-mpnet-base-v2"

data_path = glue("./")
pretrained_data_path = glue("./")

set.seed(42)


holdout <- arrow::read_feather(file = file.path(data_path, glue("ignore.{model_name}.raw.osf-bainbridge-2021-s2-0.item_correlations.feather")))

pt_holdout <- arrow::read_feather(file = file.path(data_path, glue("ignore.{pretrained_model_name}.raw.osf-bainbridge-2021-s2-0.item_correlations.feather")))

holdout_mapping_data = arrow::read_feather(
  file = file.path(data_path, glue("{model_name}.raw.osf-bainbridge-2021-s2-0.mapping2.feather"))
) %>%
  rename(scale_0 = scale0,
         scale_1 = scale1)

holdout_human_data = arrow::read_feather(
  file = file.path(data_path, glue("{model_name}.raw.osf-bainbridge-2021-s2-0.human.feather"))
)

holdout_scales <- arrow::read_feather(file.path(data_path, glue("{model_name}.raw.osf-bainbridge-2021-s2-0.scales.feather"))
)

N <- holdout_human_data %>% summarise_all(~ sum(!is.na(.))) %>% min()
total_N <- nrow(holdout_human_data)
```

The Bainbridge data was collected on N=`r total_N` respondents. The item with the most missing values still had n=`r N`.


## Synthetic inter-item correlations
```{r}
holdout_llm <- holdout %>%
  left_join(holdout_mapping_data %>% select(variable_1 = variable, InstrumentA = instrument, ScaleA = scale_0, SubscaleA = scale_1)) %>%
  left_join(holdout_mapping_data %>% select(variable_2 = variable, InstrumentB = instrument, ScaleB = scale_0, SubscaleB = scale_1))

pt_holdout_llm <- pt_holdout %>%
  left_join(holdout_mapping_data %>% select(variable_1 = variable, InstrumentA = instrument, ScaleA = scale_0, SubscaleA = scale_1)) %>%
  left_join(holdout_mapping_data %>% select(variable_2 = variable, InstrumentB = instrument, ScaleB = scale_0, SubscaleB = scale_1))
```


### Accuracy
```{r}
se2 <- mean(holdout_llm$empirical_r_se^2)

r <- broom::tidy(cor.test(holdout_llm$empirical_r, holdout_llm$synthetic_r))
pt_r <- broom::tidy(cor.test(pt_holdout_llm$empirical_r, pt_holdout_llm$synthetic_r))

model <- paste0('
  # Latent variables
  PearsonLatent =~ 1*empirical_r

  # Fixing error variances based on known standard errors
  empirical_r ~~ ',se2,'*empirical_r

  # Relationship between latent variables
  PearsonLatent ~~ synthetic_r
')

fit <- sem(model, data = holdout_llm)
pt_fit <- sem(model, data = pt_holdout_llm)

m_synth_r_items <- brm(
  bf(empirical_r | mi(empirical_r_se) ~ synthetic_r + (1|mm(variable_1, variable_2)),
     sigma ~ s(synthetic_r)), data = holdout_llm, 
  file = "ignore/m_synth_r_items_lm")

sd_synth <- sd(m_synth_r_items$data$synthetic_r)

newdata <- m_synth_r_items$data %>% select(empirical_r, synthetic_r, empirical_r_se)
epreds <- epred_draws(newdata = newdata, obj = m_synth_r_items, re_formula = NA, ndraws = 200)
preds <- predicted_draws(newdata = newdata, obj = m_synth_r_items, re_formula = NA, ndraws = 200)
epred_preds <- epreds %>% left_join(preds)
by_draw <- epred_preds %>% group_by(.draw) %>% 
  summarise(mae = mean(abs(.epred - .prediction)),
            .epred = var(.epred),
            .prediction = var(.prediction),
            sigma = sqrt(.prediction - .epred),
            latent_r = sqrt(.epred/.prediction))
rm(epred_preds)

accuracy_bayes_items <- by_draw %>% mean_hdci(latent_r)

bind_rows(
  pt_r %>% 
    mutate(model = "pre-trained", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  standardizedsolution(pt_fit) %>% 
    filter(lhs == "PearsonLatent", rhs ==  "synthetic_r") %>% 
    mutate(model = "pre-trained", kind = "latent outcome (SEM)") %>% 
    select(model, kind, accuracy = est.std, 
           conf.low = ci.lower, conf.high = ci.upper),
  r %>% 
    mutate(model = "fine-tuned", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  standardizedsolution(fit) %>% 
    filter(lhs == "PearsonLatent", rhs ==  "synthetic_r") %>% 
    mutate(model = "fine-tuned", kind = "latent outcome (SEM)") %>% 
    select(model, kind, accuracy = est.std, 
           conf.low = ci.lower, conf.high = ci.upper),
  accuracy_bayes_items %>% 
    mutate(model = "fine-tuned", kind = "latent outcome (Bayesian EIV)") %>% 
    select(model, kind, accuracy = latent_r, conf.low = .lower, conf.high = .upper)
) %>% 
  knitr::kable(digits = 2)
```


<details><summary><h4>Prediction error plot according to synthetic estimate</h4></summary>

```{r}
m_synth_r_items

pred <- conditional_effects(m_synth_r_items, method = "predict")
kable(rmse_items <- by_draw %>% mean_hdci(sigma), caption = "Average prediction error (RMSE)", digits = 2)
kable(mae_items <- by_draw %>% mean_hdci(mae), caption = "Average prediction error (MAE)", digits = 2)

plot_prediction_error_items <- plot(conditional_effects(m_synth_r_items, dpar = "sigma"), plot = F)[[1]] + 
  theme_bw() + 
  xlab("Synthetic inter-item correlation") + 
  ylab("Prediction error (sigma)") +
  geom_smooth(stat = "identity", color = "#a48500", fill = "#EDC951")

plot_prediction_error_items
```

</details>



### Scatter plot
```{r}
ggplot(holdout_llm, aes(synthetic_r, empirical_r, 
              ymin = empirical_r - empirical_r_se,
              ymax = empirical_r + empirical_r_se)) + 
  geom_abline(linetype = "dashed") +
  geom_point(color = "#00A0B0", alpha = 0.1, size = 1) +
  geom_smooth(aes(
    x = synthetic_r,
    y = estimate__,
    ymin = lower__,
    ymax = upper__,
  ), stat = "identity", 
  color = "#a48500",
  fill = "#EDC951",
  data = as.data.frame(pred$synthetic_r)) +
  xlab("Synthetic inter-item correlation") + 
  ylab("Empirical inter-item correlation") +
  theme_bw() +
  coord_fixed(xlim = c(-1,1), ylim = c(-1,1)) -> plot_items
plot_items
```

### Interactive plot
This plot shows only 2000 randomly selected item pairs to conserve memory. A [full interactive plot](2_interactive_item_plot.html) exists, but may react slowly.

```{r}
item_pair_table <- holdout_llm %>% 
   left_join(holdout_mapping_data %>% select(variable_1 = variable,
                                             item_text_1 = item_text)) %>% 
   left_join(holdout_mapping_data %>% select(variable_2 = variable,
                                             item_text_2 = item_text))

# item_pair_table %>% filter(str_length(item_text_1) < 30, str_length(item_text_2) < 30) %>% 
#   left_join(pt_holdout_llm %>% rename(synthetic_r_pt = synthetic_r)) %>% 
#   select(item_text_1, item_text_2, empirical_r, synthetic_r, synthetic_r_pt) %>% View()
rio::export(item_pair_table, "ignore/item_pair_table.feather")

(item_pair_table %>% 
  mutate(synthetic_r = round(synthetic_r, 2),
         empirical_r = round(empirical_r, 2),
         items = str_replace_all(str_c(item_text_1, "\n", item_text_2),
                                  "_+", " ")) %>% 
    sample_n(2000) %>%
ggplot(., aes(synthetic_r, empirical_r, 
              # ymin = empirical_r - empirical_r_se, 
              # ymax = empirical_r + empirical_r_se, 
              label = items)) + 
  geom_abline(linetype = "dashed") +
  geom_point(color = "#00A0B0", alpha = 0.3, size = 1) +
  xlab("Synthetic inter-item correlation") + 
  ylab("Empirical inter-item correlation") +
  theme_bw() +
  coord_fixed(xlim = c(-1,1), ylim = c(-1,1))) %>% 
  ggplotly()

item_pair_table <- item_pair_table %>% 
  mutate(empirical_r = sprintf("%.2f±%.3f", empirical_r,
                                 empirical_r_se),
           synthetic_r = sprintf("%.2f", synthetic_r)) %>% 
  select(item_text_1, item_text_2, empirical_r, synthetic_r)
rio::export(item_pair_table, "item_pair_table.xlsx")
```

<details><summary><h3>Robustness checks</h3></summary>


#### Comparing spline and polynomial models for heteroscedasticity
```{r}
m_synth_r_items_poly <- brm(
  bf(empirical_r | mi(empirical_r_se) ~ synthetic_r + (1|mm(variable_1, variable_2)),
     sigma ~ poly(synthetic_r, degree = 3)), data = holdout_llm, 
  file = "ignore/m_synth_r_items_lm_poly")

newdata <- m_synth_r_items_poly$data %>% select(empirical_r, synthetic_r, empirical_r_se)
epreds <- epred_draws(newdata = newdata, obj = m_synth_r_items_poly, re_formula = NA, ndraws = 200)
preds <- predicted_draws(newdata = newdata, obj = m_synth_r_items_poly, re_formula = NA, ndraws = 200)
epred_preds <- epreds %>% left_join(preds)
by_draw <- epred_preds %>% group_by(.draw) %>% 
  summarise(.epred = var(.epred),
            .prediction = var(.prediction),
            sigma = sqrt(.prediction - .epred),
            latent_r = sqrt(.epred/.prediction))

accuracy_bayes_items_poly <- by_draw %>% mean_hdci(latent_r)

bind_rows(
  accuracy_bayes_items %>% 
    mutate(model = "spline", kind = "latent outcome (Bayesian EIV)") %>% 
    select(model, kind, accuracy = latent_r, conf.low = .lower, conf.high = .upper),
  accuracy_bayes_items_poly %>% 
    mutate(model = "polynomial", kind = "latent outcome (Bayesian EIV)") %>% 
    select(model, kind, accuracy = latent_r, conf.low = .lower, conf.high = .upper)
) %>% 
  knitr::kable(digits = 2, caption = "Comparing spline and polynomial models for item correlations")
```

```{r}
plot_prediction_error_items_poly <- plot(conditional_effects(m_synth_r_items_poly, dpar = "sigma"), plot = F)[[1]] + 
  theme_bw() + 
  xlab("Synthetic inter-item correlation") + 
  ylab("Prediction error (sigma)") +
  geom_smooth(stat = "identity", color = "#a48500", fill = "#EDC951")

plot_prediction_error_items_poly
```


Is the accuracy lower within/across scales and instruments?

```{r}
holdout_llm %>% 
  mutate(same_instrument = if_else(InstrumentA == InstrumentB, 1, 0,0),
         same_scale = if_else(ScaleA == ScaleB, 1,0,0),
         same_subscale = if_else(same_scale & SubscaleA == SubscaleB, 1,0,0)) %>% 
  group_by(same_scale, same_instrument, same_subscale) %>% 
  summarise(broom::tidy(cor.test(synthetic_r, empirical_r)), sd_emp_r = sd(empirical_r), n = n()) %>% 
  select(same_instrument, same_scale, same_subscale, r = estimate, conf.low, conf.high, n, sd_emp_r) %>% 
  arrange(same_instrument, same_scale, same_subscale) %>% 
  kable()
```

Is the accuracy lower outside classic Big Five?

```{r}
holdout_llm %>% 
  mutate(big_five = case_when(
    str_detect(InstrumentA, "(Personality|Big Five)") & str_detect(InstrumentB, "(Personality|Big Five)") ~ "both",
    str_detect(InstrumentA, "(Personality|Big Five)") | str_detect(InstrumentB, "(Personality|Big Five)") ~ "either",
    TRUE ~ "none"
         )) %>% 
  group_by(big_five) %>% 
  summarise(broom::tidy(cor.test(synthetic_r, empirical_r)), sd_emp_r = sd(empirical_r), n = n()) %>% 
  select(big_five, r = estimate, conf.low, conf.high, n, sd_emp_r) %>% 
  arrange(big_five) %>% 
  kable()
```

Is the accuracy lower for items that have low variance?

```{r}
item_variances <- holdout_human_data %>% summarise_all(~ sd(., na.rm = T)) %>% 
  pivot_longer(everything(), names_to = "variable", values_to = "item_sd")

by_max_cov <- holdout_llm %>% 
  left_join(item_variances, by = c("variable_1" = "variable")) %>% 
  left_join(item_variances, by = c("variable_2" = "variable"), suffix = c("_1", "_2")) %>% 
  mutate(max_covariance = ceiling((item_sd_1 * item_sd_2)*10)/10)

rs_by_max_cov <- by_max_cov %>% 
  group_by(max_covariance) %>% 
  filter(n() > 3) %>% 
  summarise(broom::tidy(cor.test(synthetic_r, empirical_r)), sd_emp_r = sd(empirical_r), n = n()) %>% 
  select(max_covariance, r = estimate, conf.low, conf.high, n, sd_emp_r) %>% 
  arrange(max_covariance)

rs_by_max_cov%>% 
  kable()
rs_by_max_cov %>% ggplot(aes(max_covariance, r, ymin = conf.low, ymax = conf.high)) +
  geom_pointrange()

by_max_cov%>% 
  filter(max_covariance > .7) %>% 
  summarise(broom::tidy(cor.test(synthetic_r, empirical_r)), sd_emp_r = sd(empirical_r), n = n()) %>% 
  kable()

holdout_llm %>% 
  left_join(item_variances, by = c("variable_1" = "variable")) %>% 
  left_join(item_variances, by = c("variable_2" = "variable"), suffix = c("_1", "_2")) %>% 
  mutate(max_covariance = ceiling((item_sd_1 * item_sd_2)*10)/10) %>% 
  filter(max_covariance > 1) %>% 
  summarise(broom::tidy(cor.test(synthetic_r, empirical_r)), sd_emp_r = sd(empirical_r), n = n()) %>% 
  select(r = estimate, conf.low, conf.high, n, sd_emp_r) %>% 
  knitr::kable()
```

#### Averages
```{r}
holdout_llm %>% summarise(
  mean(synthetic_r),
  mean(empirical_r),
  mean(abs(synthetic_r)),
  mean(abs(empirical_r)),
  prop_negative = sum(empirical_r < 0)/n(),
  prop_pos = sum(empirical_r > 0)/n(),
  `prop_below_-.10` = sum(empirical_r < -0.1)/n(),
  `prop_above_.10` = sum(empirical_r > 0.1)/n(),
) %>% kable(digits = 2, caption = "Average correlations")
```

Is the accuracy lower for the pre-trained model?

```{r}
ggplot(pt_holdout_llm, aes(synthetic_r, empirical_r, 
              ymin = empirical_r - empirical_r_se,
              ymax = empirical_r + empirical_r_se)) + 
  geom_abline(linetype = "dashed") +
  geom_point(color = "#00A0B0", alpha = 0.1, size = 1) +
  xlab("Synthetic inter-item correlation") + 
  ylab("Empirical inter-item correlation") +
  theme_bw() +
  coord_fixed(xlim = c(-1,1), ylim = c(-1,1)) -> pt_plot_items
pt_plot_items
```


</details>



[Full table of synthetic and empirical item pair correlations](item_pair_table.xlsx)


## Synthetic Reliabilities
```{r}

scales <- read_rds(file = file.path(data_path, glue("ignore.scales_with_alpha_se.rds")))


source("global_functions.R")

scales <- scales %>% filter(number_of_items >= 3)
```


### Accuracy
```{r}
se2 <- mean(scales$empirical_alpha_se^2)
r <- broom::tidy(cor.test(scales$empirical_alpha, scales$synthetic_alpha))
pt_r <- broom::tidy(cor.test(scales$empirical_alpha, scales$pt_synthetic_alpha))

model <- paste0('
  # Latent variables
  latent_real_rel =~ 1*empirical_alpha

  # Fixing error variances based on known standard errors
  empirical_alpha ~~ ',se2,'*empirical_alpha

  # Relationship between latent variables
  latent_real_rel ~~ synthetic_alpha
')

fit <- sem(model, data = scales)
pt_fit <- sem(model, data = scales %>% 
                select(empirical_alpha, synthetic_alpha = pt_synthetic_alpha))

m_lmsynth_rel_scales <- brm(
  bf(empirical_alpha | mi(empirical_alpha_se) ~ synthetic_alpha,
     sigma ~ s(synthetic_alpha)), data = scales, 
  file = "ignore/m_synth_rel_lm")

newdata <- m_lmsynth_rel_scales$data %>% select(empirical_alpha, synthetic_alpha, empirical_alpha_se)
epreds <- epred_draws(newdata = newdata, obj = m_lmsynth_rel_scales, re_formula = NA)
preds <- predicted_draws(newdata = newdata, obj = m_lmsynth_rel_scales, re_formula = NA)
epred_preds <- epreds %>% left_join(preds)
by_draw <- epred_preds %>% group_by(.draw) %>% 
  summarise(.epred = var(.epred),
            .prediction = var(.prediction),
            sigma = sqrt(.prediction - .epred),
            latent_r = sqrt(.epred/.prediction))

accuracy_bayes_rels <- by_draw %>% mean_hdci(latent_r)

bind_rows(
  pt_r %>% 
    mutate(model = "pre-trained", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  standardizedsolution(pt_fit) %>% 
    filter(lhs == "latent_real_rel", rhs ==  "synthetic_alpha") %>% 
    mutate(model = "pre-trained", kind = "latent outcome (SEM)") %>% 
    select(model, kind, accuracy = est.std, 
           conf.low = ci.lower, conf.high = ci.upper),
  r %>% 
    mutate(model = "fine-tuned", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  standardizedsolution(fit) %>% 
    filter(lhs == "latent_real_rel", rhs ==  "synthetic_alpha") %>% 
    mutate(model = "fine-tuned", kind = "latent outcome (SEM)") %>% 
    select(model, kind, accuracy = est.std, 
           conf.low = ci.lower, conf.high = ci.upper),
  accuracy_bayes_rels %>% 
    mutate(model = "fine-tuned", kind = "latent outcome (Bayesian EIV)") %>% 
    select(model, kind, accuracy = latent_r, conf.low = .lower, conf.high = .upper)
  ) %>% 
  knitr::kable(digits = 2)
```


<details><summary><h4>Prediction error plot according to synthetic estimate</h4></summary>

```{r}
m_lmsynth_rel_scales

pred <- conditional_effects(m_lmsynth_rel_scales, method = "predict")
kable(rmse_alpha <- by_draw %>% mean_hdci(sigma), caption = "Average prediction error (RMSE)", digits = 2)

plot_prediction_error_alpha <- plot(conditional_effects(m_lmsynth_rel_scales, dpar = "sigma"), plot = F)[[1]] + 
  theme_bw() + 
  geom_smooth(stat = "identity", color = "#a48500", fill = "#EDC951") + 
  xlab("Synthetic Cronbach's alpha") + 
  ylab("Prediction error (sigma)") +
  coord_cartesian(xlim = c(-1, 1), ylim = c(0, 0.35))
plot_prediction_error_alpha
```

</details>




### Scatter plot
```{r}
ggplot(scales, aes(synthetic_alpha, empirical_alpha, 
                   color = str_detect(scale, "^random"), 
              ymin = empirical_alpha - empirical_alpha_se,
              ymax = empirical_alpha + empirical_alpha_se)) + 
  geom_abline(linetype = "dashed") +
  geom_point(alpha = 0.6, size = 1) +
  geom_smooth(aes(
    x = synthetic_alpha,
    y = estimate__,
    ymin = lower__,
    ymax = upper__,
  ), stat = "identity", 
  color = "#a48500",
  fill = "#EDC951",
  data = as.data.frame(pred$synthetic_alpha)) +
  scale_color_manual(values = c("#00A0B0", "#6A4A3C"),
                     guide = "none") +
  xlab("Synthetic Cronbach's alpha") + 
  ylab("Empirical Cronbach's alpha") +
  theme_bw() +
  coord_fixed(xlim = c(-1,1), ylim = c(-1,1)) -> plot_rels
plot_rels
```

### Interactive plot
```{r}
(scales %>% 
  filter(type == "real") %>% 
  mutate(synthetic_alpha = round(synthetic_alpha, 2),
         empirical_alpha = round(empirical_alpha, 2),
         scale = str_replace_all(scale, "_+", " ")) %>% 
ggplot(., aes(synthetic_alpha, empirical_alpha, 
              # ymin = empirical_r - empirical_r_se, 
              # ymax = empirical_r + empirical_r_se, 
              label = scale)) + 
  geom_abline(linetype = "dashed") +
  geom_point(alpha = 0.3, size = 1, color = "#00A0B0") +
  xlab("Synthetic Cronbach's alpha") + 
  ylab("Empirical Cronbach's alpha") +
  theme_bw() +
  theme(legend.position='none') + 
  coord_fixed(xlim = c(NA,1), ylim = c(NA,1))) %>% 
  ggplotly()
```

<details><summary><h4>Table</h4></summary>

```{r}
scales %>% 
  filter(type != "random") %>% 
  mutate(empirical_alpha = sprintf("%.2f±%.3f", empirical_alpha,
                               empirical_alpha_se),
         synthetic_alpha = sprintf("%.2f", synthetic_alpha),
         scale = str_replace_all(scale, "_+", " ")
         ) %>% 
  select(scale, empirical_alpha, synthetic_alpha, number_of_items) %>% 
  DT::datatable(rownames = FALSE,
                filter = "top")

scales %>% ungroup() %>% 
  summarise(mean(empirical_alpha), sd(empirical_alpha))
scales %>% group_by(type) %>% 
  summarise(mean(empirical_alpha), sd(empirical_alpha),
            cor = broom::tidy(cor.test(synthetic_alpha, empirical_alpha)), n())
psychometric::cRRr(0.632, 0.0992, 0.235)
```

</details>



<details><summary><h3>Robustness checks</h3></summary>

#### Accuracy by whether scales were real or random
The SurveyBot3000 does not "know" whether scales were published in the literature or formed at random. Knowing what we do about the research literature in psychology, we can infer that published scales will usually exceed the Nunnally threshold of .70. Hence, we know that the synthetic alphas for published scales should rarely be below .70. If we regress synthetic alphas on empirical alphas separately for the scales taken from the literature, we see this as a bias (a positive regression intercept of .68 and a slope ≠ 1, .26). Still, the synthetic alpha estimates are predictive of empirical alphas with an accuracy of .65. 

There is no clear bias for the random scales. When both are analyzed jointly, the clear selection bias for the published scales is mostly averaged out but is reflected in the slope exceeding 1.

```{r}
scales %>% 
  group_by(type) %>% 
  summarise(broom::tidy(cor.test(synthetic_alpha, empirical_alpha)), sd_alpha = sd(empirical_alpha), n = n()) %>% 
  knitr::kable(digits = 2, caption = "Accuracy shown separately for randomly formed and real scales")
```

```{r}
scales %>% 
  group_by(type) %>% 
  summarise(broom::tidy(lm(empirical_alpha ~ synthetic_alpha)), n = n()) %>% 
  knitr::kable(digits = 2, caption = "Regression intercepts and slopes for randomly formed and real scales")
```

#### As in our Stage 1 submission
Here are the results if we calculate the accuracy and prediction error as in the Stage 1 submission. We now think this approach, by conditioning on random variation in the empirical correlations, gave a misleading picture of the accuracy and bias of the synthetic Cronbach's alphas. Here we report the results if we conduct the analysis as in Stage 1 (but with the corrected SE of empirical alphas).

```{r}
s1_scales <- scales %>%
  filter(number_of_items > 2) %>% 
  rowwise() %>%
  mutate(reverse_items = if_else(type == "random", list(reverse_items_by_1st), list(reverse_items)),
         r_real_rev = list(reverse_items(r_real, reverse_items)),
         pt_r_llm_rev = list(reverse_items(pt_r_llm, reverse_items)),
         r_llm_rev = list(reverse_items(r_llm, reverse_items))) %>%
  mutate(
    rel_real = list(psych::alpha(r_real_rev, keys = F, n.obs = N)$feldt),
    rel_llm = list(psych::alpha(r_llm_rev, keys = F, n.obs = N)$feldt),
    rel_pt_llm = list(psych::alpha(pt_r_llm_rev, keys = F, n.obs = N)$feldt)) %>%
  mutate(empirical_alpha = rel_real$alpha$raw_alpha,
         synthetic_alpha = rel_llm$alpha$raw_alpha,
         pt_synthetic_alpha = rel_pt_llm$alpha$raw_alpha) %>%
  mutate(
    empirical_alpha_se = mean(diff(unlist(psychometric::alpha.CI(empirical_alpha, k = number_of_items, N = N, level = 0.95))))/1.96) %>% 
      filter(empirical_alpha > 0)

s1_r <- broom::tidy(cor.test(s1_scales$empirical_alpha, s1_scales$synthetic_alpha))
s1_pt_r <- broom::tidy(cor.test(s1_scales$empirical_alpha, s1_scales$pt_synthetic_alpha))
                             
bind_rows(
  s1_pt_r %>% 
    mutate(model = "pre-trained", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  s1_r %>% 
    mutate(model = "fine-tuned", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  ) %>% 
  knitr::kable(digits = 2, caption = "Accuracy of synthetic alphas when empirical alphas are biased upward through adaptive item reversion and selection on positive alphas")
```


```{r}
m_lmsynth_rel_scales_s1 <- brm(
  bf(empirical_alpha | mi(empirical_alpha_se) ~ synthetic_alpha,
     sigma ~ poly(synthetic_alpha, degree = 3)), data = s1_scales, 
  iter = 6000, control = list(adapt_delta = 0.9),
  file = "ignore/m_synth_rel_lm_as_stage_1")

pred <- conditional_effects(m_lmsynth_rel_scales_s1, method = "predict")
ggplot(s1_scales, aes(synthetic_alpha, empirical_alpha, 
                   color = str_detect(scale, "^random"), 
              ymin = empirical_alpha - empirical_alpha_se,
              ymax = empirical_alpha + empirical_alpha_se)) + 
  geom_abline(linetype = "dashed") +
  geom_point(alpha = 0.6, size = 1) +
  geom_smooth(aes(
    x = synthetic_alpha,
    y = estimate__,
    ymin = lower__,
    ymax = upper__,
  ), stat = "identity", 
  color = "#a48500",
  fill = "#EDC951",
  data = as.data.frame(pred$synthetic_alpha)) +  scale_color_manual(values = c("#00A0B0", "#6A4A3C"),
                     guide = "none") +
  xlab("Synthetic Cronbach's alpha") + 
  ylab("Empirical Cronbach's alpha") +
  theme_bw() +
  coord_fixed(xlim = c(-1, 1), ylim = c(-1,1))  -> s1_plot_rels
s1_plot_rels


newdata <- m_lmsynth_rel_scales_s1$data %>% select(empirical_alpha, synthetic_alpha, empirical_alpha_se)
epreds <- epred_draws(newdata = newdata, obj = m_lmsynth_rel_scales_s1, re_formula = NA)
preds <- predicted_draws(newdata = newdata, obj = m_lmsynth_rel_scales_s1, re_formula = NA)
epred_preds <- epreds %>% left_join(preds)
by_draw <- epred_preds %>% group_by(.draw) %>% 
  summarise(
             mae = mean(abs(.epred - .prediction)),
            .epred = var(.epred),
            .prediction = var(.prediction),
            sigma = sqrt(.prediction - .epred),
            latent_r = sqrt(.epred/.prediction))

accuracy_bayes_rels_poly <- by_draw %>% mean_hdci(latent_r)

s1_plot_rels
```

```{r}
bind_rows(
  r %>% 
    mutate(model = "fine-tuned", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  s1_r %>% 
    mutate(model = "fine-tuned, conditioned on empirical r", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  accuracy_bayes_rels %>% 
    mutate(model = "fine-tuned", kind = "latent outcome (Bayesian EIV)") %>% 
    select(model, kind, accuracy = latent_r, conf.low = .lower, conf.high = .upper),
  accuracy_bayes_rels_poly %>% 
    mutate(model = "fine-tuned, conditioned on empirical r", kind = "latent outcome (Bayesian EIV)") %>% 
    select(model, kind, accuracy = latent_r, conf.low = .lower, conf.high = .upper),
  ) %>% 
  knitr::kable(digits = 2, caption = "Accuracy of synthetic alphas when empirical alphas are biased upward through adaptive item reversion and selection on positive alphas")
```



#### Number of items as a trivial predictor

Although the number of items alone can of course predict Cronbach's alpha, the synthetic alphas explain much more variance in empirical alphas.

```{r}
scales %>% 
  ungroup() %>% 
  summarise(broom::tidy(cor.test(number_of_items, empirical_alpha)), sd_alpha = sd(empirical_alpha), n = n()) %>% 
  knitr::kable()


summary(lm(empirical_alpha ~ number_of_items, scales))
summary(lm(empirical_alpha ~ number_of_items + synthetic_alpha, scales))
```



Is the accuracy lower for the pre-trained model?

```{r}
ggplot(scales, aes(pt_synthetic_alpha, empirical_alpha, 
                   color = str_detect(scale, "^random"), 
              ymin = empirical_alpha - empirical_alpha_se,
              ymax = empirical_alpha + empirical_alpha_se)) + 
  geom_abline(linetype = "dashed") +
  geom_point(alpha = 0.6, size = 1) +
  scale_color_manual(values = c("#00A0B0", "#6A4A3C"),
                     guide = "none") +
  xlab("Synthetic Cronbach's alpha") + 
  ylab("Empirical Cronbach's alpha") +
  theme_bw() +
  coord_fixed(xlim = c(-1,1), ylim = c(-1,1)) -> pt_plot_rels
pt_plot_rels
```


</details>




## Synthetic Scale Correlations
```{r}
manifest_scores = arrow::read_feather(file = file.path(data_path, glue("ignore.{model_name}.raw.osf-bainbridge-2021-s2-0.scale_correlations.feather")))
pt_manifest_scores = arrow::read_feather(file = file.path(data_path, glue("ignore.{pretrained_model_name}.raw.osf-bainbridge-2021-s2-0.scale_correlations.feather")))

n_distinct(manifest_scores$scale_a)

manifest_scores <- manifest_scores %>%
 left_join(scales, by = c("scale_a" = "scale")) %>%
 left_join(scales, by = c("scale_b" = "scale"))
```

### Accuracy
```{r}
r <- broom::tidy(cor.test(manifest_scores$empirical_r, manifest_scores$synthetic_r))
pt_r <- broom::tidy(cor.test(pt_manifest_scores$empirical_r, pt_manifest_scores$synthetic_r))

se2 <- mean(manifest_scores$empirical_r_se^2)
model <- paste0('
    # Latent variables
    PearsonLatent =~ 1*empirical_r

    # Fixing error variances based on known standard errors
    empirical_r ~~ ',se2,'*empirical_r

    # Relationship between latent variables
    PearsonLatent ~~ synthetic_r
  ')

fit <- sem(model, data = manifest_scores)
pt_fit <- sem(model, data = pt_manifest_scores)


m_lmsynth_r_scales <- brm(
  bf(empirical_r | mi(empirical_r_se) ~ synthetic_r + (1|mm(scale_a, scale_b)),
     sigma ~ s(synthetic_r)), data = manifest_scores, 
  file = "ignore/m_synth_r_scales_lm8")

sd_synth <- sd(m_lmsynth_r_scales$data$synthetic_r)


newdata <- m_lmsynth_r_scales$data %>% select(empirical_r, synthetic_r, empirical_r_se)
epreds <- epred_draws(newdata = newdata, obj = m_lmsynth_r_scales, re_formula = NA)
preds <- predicted_draws(newdata = newdata, obj = m_lmsynth_r_scales, re_formula = NA)
epred_preds <- epreds %>% left_join(preds)
by_draw <- epred_preds %>% group_by(.draw) %>% 
  summarise(.epred = var(.epred),
            .prediction = var(.prediction),
            sigma = sqrt(.prediction - .epred),
            latent_r = sqrt(.epred/.prediction))

accuracy_bayes_scales <- by_draw %>% mean_hdci(latent_r)

bind_rows(
  pt_r %>% 
    mutate(model = "pre-trained", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  standardizedsolution(pt_fit) %>% 
    filter(lhs == "PearsonLatent", rhs ==  "synthetic_r") %>% 
    mutate(model = "pre-trained", kind = "latent outcome (SEM)") %>% 
    select(model, kind, accuracy = est.std, 
           conf.low = ci.lower, conf.high = ci.upper),
  r %>% 
    mutate(model = "fine-tuned", kind = "manifest") %>% 
    select(model, kind, accuracy = estimate, conf.low, conf.high),
  standardizedsolution(fit) %>% 
    filter(lhs == "PearsonLatent", rhs ==  "synthetic_r") %>% 
    mutate(model = "fine-tuned", kind = "latent outcome (SEM)") %>% 
    select(model, kind, accuracy = est.std, 
           conf.low = ci.lower, conf.high = ci.upper),
  accuracy_bayes_scales %>% 
    mutate(model = "fine-tuned", kind = "latent outcome (Bayesian EIV)") %>% 
    select(model, kind, accuracy = latent_r, conf.low = .lower, conf.high = .upper)
  ) %>% 
  knitr::kable(digits = 2)
```


<details><summary><h4>Prediction error plot according to synthetic estimate</h4></summary>

```{r}
m_lmsynth_r_scales
kable(rmse_scales <- by_draw %>% mean_hdci(sigma), caption = "Average prediction error (RMSE)", digits = 2)


pred <- conditional_effects(m_lmsynth_r_scales, method = "predict")
plot_prediction_error_scales <- plot(conditional_effects(m_lmsynth_r_scales, dpar = "sigma"), plot = F)[[1]] + 
  theme_bw() + 
  geom_smooth(stat = "identity", color = "#a48500", fill = "#EDC951") + 
  xlab("Synthetic inter-scale correlation") + 
  ylab("Prediction error (sigma)")
plot_prediction_error_scales
```


</details>



### Scatter plot
```{r}
ggplot(manifest_scores, aes(synthetic_r, empirical_r, 
              ymin = empirical_r - empirical_r_se,
              ymax = empirical_r + empirical_r_se)) + 
  geom_abline(linetype = "dashed") +
  geom_point(color = "#00A0B0", alpha = 0.3, size = 1) +
  geom_smooth(aes(
    x = synthetic_r,
    y = estimate__,
    ymin = lower__,
    ymax = upper__,
  ), stat = "identity", 
  color = "#a48500",
  fill = "#EDC951",
  data = as.data.frame(pred$synthetic_r)) +
  xlab("Synthetic inter-scale correlation") + 
  ylab("Empirical inter-scale correlation") +
  theme_bw() +
  coord_fixed(xlim = c(-1,1), ylim = c(-1,1)) -> plot_scales
plot_scales
```

### Interactive plot
```{r}
(manifest_scores %>% 
  mutate(synthetic_r = round(synthetic_r, 2),
         empirical_r = round(empirical_r, 2),
         scales = str_replace_all(str_c(scale_a, "\n", scale_b),
                                  "_+", " ")) %>% 
ggplot(., aes(synthetic_r, empirical_r, 
              # ymin = empirical_r - empirical_r_se, 
              # ymax = empirical_r + empirical_r_se, 
              label = scales)) + 
  geom_abline(linetype = "dashed") +
  geom_point(color = "#00A0B0", alpha = 0.3, size = 1) +
  xlab("Synthetic inter-scale correlation") + 
  ylab("Empirical inter-scale correlation") +
  theme_bw() +
  coord_fixed(xlim = c(-1,1), ylim = c(-1,1))) %>% 
  ggplotly()
```

<details><summary>Table</summary>

```{r}
manifest_scores %>% 
                mutate(empirical_r = sprintf("%.2f±%.3f", empirical_r,
                                             empirical_r_se),
                       synthetic_r = sprintf("%.2f", synthetic_r),
                       scale_a = str_replace_all(scale_a, "_+", " "),
                       scale_b = str_replace_all(scale_b, "_+", " ")
                       ) %>% 
                select(scale_a, scale_b, empirical_r, synthetic_r) %>% 
  DT::datatable(rownames = FALSE,
                filter = "top")
```

</details>




<details><summary><h3>Robustness checks</h3></summary>


#### Comparing spline and polynomial models for heteroscedasticity
```{r}
m_lmsynth_r_scales_poly <- brm(
  bf(empirical_r | mi(empirical_r_se) ~ synthetic_r + (1|mm(scale_a, scale_b)),
     sigma ~ poly(synthetic_r, degree = 3)), data = manifest_scores, 
  file = "ignore/m_synth_r_scales_lm_poly")

newdata <- m_lmsynth_r_scales_poly$data %>% select(empirical_r, synthetic_r, empirical_r_se)
epreds <- epred_draws(newdata = newdata, obj = m_lmsynth_r_scales_poly, re_formula = NA)
preds <- predicted_draws(newdata = newdata, obj = m_lmsynth_r_scales_poly, re_formula = NA)
epred_preds <- epreds %>% left_join(preds)
by_draw <- epred_preds %>% group_by(.draw) %>% 
  summarise(.epred = var(.epred),
            .prediction = var(.prediction),
            sigma = sqrt(.prediction - .epred),
            latent_r = sqrt(.epred/.prediction))

accuracy_bayes_scales_poly <- by_draw %>% mean_hdci(latent_r)

bind_rows(
  accuracy_bayes_scales %>% 
    mutate(model = "spline", kind = "latent outcome (Bayesian EIV)") %>% 
    select(model, kind, accuracy = latent_r, conf.low = .lower, conf.high = .upper),
  accuracy_bayes_scales_poly %>% 
    mutate(model = "polynomial", kind = "latent outcome (Bayesian EIV)") %>% 
    select(model, kind, accuracy = latent_r, conf.low = .lower, conf.high = .upper)
) %>% 
  knitr::kable(digits = 2, caption = "Comparing spline and polynomial models for scale correlations")
```


```{r}
plot_prediction_error_scales_poly <- plot(conditional_effects(m_lmsynth_r_scales_poly, dpar = "sigma"), plot = F)[[1]] + 
  theme_bw() + 
  geom_smooth(stat = "identity", color = "#a48500", fill = "#EDC951") + 
  xlab("Synthetic inter-scale correlation") + 
  ylab("Prediction error (sigma)")
plot_prediction_error_scales_poly
```


#### How does number of items across the two scales relate to accuracy?

```{r}
by_item_number <- manifest_scores %>%
  mutate(items = number_of_items.x + number_of_items.y) %>%
  group_by(items) %>%
  summarise(broom::tidy(cor.test(empirical_r, synthetic_r)), pairwise_n = n()) 

by_item_number %>% 
  ggplot(aes(items, estimate, ymin = conf.low, ymax = conf.high)) + 
  geom_pointrange() +
  scale_y_continuous("Manifest accuracy (with 95% confidence interval)") +
  xlab("Number of items summed across scales")

lm(estimate ~ items, by_item_number, weights = 1/(by_item_number$conf.high-by_item_number$conf.low))

manifest_scores %>%
  filter(number_of_items.x >= 10, number_of_items.y >= 10) %>%
  summarise(cor = cor(empirical_r, synthetic_r), n())
```


#### Averages
```{r}
scales %>% filter(type == "real") %>% ungroup() %>% 
  filter(number_of_items >= 3) %>% 
  summarise(median(number_of_items),
            mean(number_of_items))
```



#### Is the accuracy lower for the pre-trained model?

```{r}
ggplot(pt_manifest_scores, aes(synthetic_r, empirical_r, 
              ymin = empirical_r - empirical_r_se,
              ymax = empirical_r + empirical_r_se)) + 
  geom_abline(linetype = "dashed") +
  geom_point(color = "#00A0B0", alpha = 0.3, size = 1) +
  xlab("Synthetic inter-scale correlation") + 
  ylab("Empirical inter-scale correlation") +
  theme_bw() +
  coord_fixed(xlim = c(-1,1), ylim = c(-1,1)) -> pt_plot_scales
pt_plot_scales
```


</details>




## Combined plot

```{r fig.width = 8.3, fig.height = 6}


get_scale_point <- function(data, synthetic_approx, empirical_approx) {
  data %>%
    ungroup() %>% 
    # Find closest point to target coordinates
    mutate(dist = sqrt((synthetic_alpha - synthetic_approx)^2 + 
                      (empirical_alpha - empirical_approx)^2)) %>%
    arrange(dist) %>%
    slice(1) %>%
    select(synthetic_alpha, empirical_alpha)
}
get_scale_point_by_name <- function(data, name) {
  data %>%
    filter(scale == name) %>%
    slice(1) %>%
    select(synthetic_alpha, empirical_alpha, pt_synthetic_alpha)
}
ipip_e <- get_scale_point_by_name(scales, "International_Personality_Item_Pool_120_extraversion")
lot_o <- get_scale_point_by_name(scales, "Life_Orientation_Test_Optimism")
# get_scale_point_by_name <- function(data, var_1, var_2) {
#   data %>%
#     filter(variable_1 == scale_name) %>% 
#     select(synthetic_r, empirical_r)
# }

library(patchwork)
pt_plot_items2 <- pt_plot_items +
    annotate("text", size = 2.5, x = 0.5, y = -0.8, vjust = 1, hjust = 1, label = "r(I fear for the worst,\nI never worry about anything)", color = "#00A0B0") +
  annotate("segment", x = 0, y = -0.78, xend = 0.2761906, yend = -0.3459711, color = "#00A0B0", alpha = 0.7) +
  annotate("text", size = 2.5, x = -.1, y = 0.5, hjust = 1, label = "r(I get angry easily,\nI lose my temper)", color = "#00A0B0") + 
  annotate("segment", x = -.1, y = 0.5, xend = 0.6935711, yend = 0.7140546, color = "#00A0B0", alpha = 0.7)
  

plot_items2 <- plot_items +
  annotate("text", size = 3, x = -1, y = 0.98, vjust = 0, hjust = 0, label = with(accuracy_bayes_items, { sprintf("accuracy = %.2f [%.2f;%.2f]", latent_r, .lower, .upper) })) +
  annotate("text", size = 2.5, x = 0.5, y = -0.8, vjust = 1, hjust = 1, label = "r(I fear for the worst,\nI never worry about anything)", color = "#00A0B0") +
  annotate("segment", x = 0, y = -0.78, xend = -0.1104686, yend = -0.3459711, color = "#00A0B0", alpha = 0.7) +
  annotate("text", size = 2.5, x = -.1, y = 0.5, hjust = 1, label = "r(I get angry easily,\nI lose my temper)", color = "#00A0B0") + 
  annotate("segment", x = -.1, y = 0.5, xend = 0.8031979, yend = 0.7140546, color = "#00A0B0", alpha = 0.7)
  # annotate("text", size = 2.5, x = -0.5, y = -0.8, hjust = 0, label = "r(I love life,\nI avoid crowds)", color = "#00A0B0") +
  # annotate("segment", x = -.3, y = -0.7, xend = -0.23, yend = -0.28, color = "#00A0B0", alpha = 0.7) +
  # annotate("text", size = 2.5, x = -.3, y = 0.5, hjust = 1, label = "r(I work hard,\nI am diligent)", color = "#00A0B0") +
  # annotate("segment", x = -.3, y = .5, xend = .52, yend = .58, color = "#00A0B0", alpha = 0.7)


pt_plot_rels2 <- pt_plot_rels + 
  annotate("text", size = 2.5, x = 0.21, y = -0.2, hjust = 0, label = "IPIP Extraversion", color = "#00A0B0") +
  annotate("segment", x = 0.75, y = -0.2, xend = 0.87, yend = 0.90, color = "#00A0B0", alpha = 0.7) +
  annotate("text", size = 2.5, x = -0.02, y = 0.95, hjust = 0, label = "LOT Optimism", color = "#00A0B0") +
  annotate("segment", x = 0.11, y = 0.93, xend = -1.477226, yend = 0.71, color = "#00A0B0", alpha = 0.7)

p1 <- get_scale_point(scales, 0.30, 0.22)
p2 <- get_scale_point(scales, 0.12, -0.36) 
p3 <- get_scale_point(scales, -0.4, -0.90)


plot_rels2 <- plot_rels + 
  annotate("text", size = 3, x = -1, y = 0.98, vjust = 0, hjust = 0, 
           label = with(accuracy_bayes_rels, { sprintf("accuracy = %.2f [%.2f;%.2f]", latent_r, .lower, .upper) })) +
  annotate("text", size = 2.5, x = -0.2, y = -0.9, hjust = 0, label = "randomly formed scales", color = "#6A4A3C") +
  annotate("segment", x = 0.4, y = -0.85, xend = p1$synthetic_alpha, yend = p1$empirical_alpha, color = "#6A4A3C", alpha = 0.7) +
  annotate("segment", x = 0.4, y = -0.85, xend = p2$synthetic_alpha, yend = p2$empirical_alpha, color = "#6A4A3C", alpha = 0.7) +
  annotate("segment", x = 0.4, y = -0.85, xend = p3$synthetic_alpha, yend = p3$empirical_alpha, color = "#6A4A3C", alpha = 0.7) +

  annotate("text", size = 2.5, x = 0.21, y = -0.2, hjust = 0, label = "IPIP Extraversion", color = "#00A0B0") +
  annotate("segment", x = 0.75, y = -0.2, xend = 0.87, yend = 0.90, color = "#00A0B0", alpha = 0.7) +
  annotate("text", size = 2.5, x = -0.32, y = 0.86, hjust = 0, label = "LOT Optimism", color = "#00A0B0") +
  annotate("segment", x = 0, y = 0.83, xend = 0.49, yend = 0.71, color = "#00A0B0", alpha = 0.7)

pt_plot_scales2 <- pt_plot_scales +
  annotate("text", size = 2.5, x = -0.2, y = 0.8, hjust = 1, label = "r(BFI Neuroticism,\nIPIP Neuroticism)", color = "#00A0B0") +
  annotate("segment", x = -.2, y = 0.8, xend = 0.22, yend = .84, color = "#00A0B0", alpha = 0.7) +
  annotate("text", size = 2.5, x = -.1, y = -0.9, hjust = 0, label = "r(BFI Depression facet,\nLOT Optimism)", color = "#00A0B0") +
  annotate("segment", x = -.1, y = -.9, xend = -0.17, yend = -.63, color = "#00A0B0", alpha = 0.7)


plot_scales2 <- plot_scales +
  annotate("text", size = 3, x = -1, y = 0.98, vjust = 0, hjust = 0, label = with(accuracy_bayes_scales, { sprintf("accuracy = %.2f [%.2f;%.2f]", latent_r, .lower, .upper) })) +
  annotate("text", size = 2.5, x = -0.1, y = 0.5, hjust = 1, label = "r(BFI Neuroticism,\nIPIP Neuroticism)", color = "#00A0B0") +
  annotate("segment", x = -.1, y = 0.5, xend = .84, yend = .84, color = "#00A0B0", alpha = 0.7) +
  annotate("text", size = 2.5, x = -.15, y = -0.7, hjust = 0, label = "r(BFI Depression facet,\nLOT Optimism)", color = "#00A0B0") +
  annotate("segment", x = -.15, y = -.7, xend = -.34, yend = -.63, color = "#00A0B0", alpha = 0.7)


(pt_plot_items2  + ggtitle("Pre-trained model before domain adaptation and fine-tuning")+
    pt_plot_rels2 +
    pt_plot_scales2) /


(plot_items2 + ggtitle("SurveyBot 3000") +
    plot_rels2  +
    plot_scales2)

ggsave("Figure_pilot.pdf", width = 8.3, height = 6, device = grDevices::cairo_pdf)
ggsave("Figure_pilot.png", width = 8.3, height = 6)



# ggsave("ignore/Figure_pilot.svg", width = 8.3, height = 5.5, device = svglite::svglite)
```

### Prediction error plots
```{r fig.width = 8.3, fig.height = 3}
library(patchwork)

(plot_prediction_error_items + 
    coord_cartesian(xlim = c(-1, 1), ylim = c(0, 0.4)) +
    annotate("text", size = 3, x = -1, y = 0.4, vjust = 0, hjust = 0, label = with(rmse_items, { sprintf("RMSE = %.2f [%.2f;%.2f]", sigma, .lower, .upper) })) +
    
    plot_prediction_error_alpha + 
    coord_cartesian(xlim = c(-1, 1), ylim = c(0, 0.4))  +
    annotate("text", size = 3, x = -1, y = 0.4, vjust = 0, hjust = 0, label = with(rmse_alpha, { sprintf("RMSE = %.2f [%.2f;%.2f]", sigma, .lower, .upper) })) +
    
    plot_prediction_error_scales + 
    coord_cartesian(xlim = c(-1, 1), ylim = c(0, 0.4)) +
    annotate("text", size = 3, x = -1, y = 0.4, vjust = 0, hjust = 0, label = with(rmse_scales, { sprintf("RMSE = %.2f [%.2f;%.2f]", sigma, .lower, .upper) }))
)

ggsave("ignore/Figure_prediction_error_pilot.pdf", width = 8.3, height = 3, device = grDevices::cairo_pdf)
ggsave("ignore/Figure_prediction_error_pilot.png", width = 8.3, height = 3)
```


